Allee Effect in Cultural Evolution

### 2015-10-01 manuscript/draft.tex
acknowledgements

>>>>

\section{Acknowledgements}

ERC was funded by a Marie-Curie Intra-European Fellowship (grant 625863). XRC is part of the SimulPast Project (CSD2010-00034) funded by the CONSOLIDER-INGENIO2010 program of the Ministry of Science and Innovation—Spain. Experiments were run using the MareNostrum 3 supercomputer at the Barcelona Supercomputing Centre facility.
